### 2019-06-15 2-Chapters/4-Chapter/chapter4.tex
Rien de neuf
Typo

\abstractStartChapter{}%
%
In this Chapter~\ref{chapter:4}, we propose two models of Internet of Things (IoT) networks, composed of many independent IoT end-devices,
that can use low-cost RL (Reinforcement Learning) algorithms to learn to improve their spectrum access.
%
Decentralized RL for IoT lets the devices use acknowledgements sent by their Base Station as a reward, instead of sensing feedback like for OSA.
We consider many independent ``dynamic'' devices, communicating with a small probability at every instant.
Simulations show that dynamic devices can improve their spectrum efficiency,
by using MAB algorithms like \UCB.
% in the case of a non-uniform repartition of the static devices in the channels
We also developed a proof-of-concept using USRP platforms, for a real-world validation of this approach.
% Numerical simulations justify the interest of the approach,
%  of the advantage of using MAB algorithms for the first model.
%
% On a simple example, we present in Section~\ref{sec:4:gnuradio} a demonstration that implements and validates the proposed approach, using real wireless radio hardware.
The first model
% without retransmission of packets,
is interesting for its simplicity,
and because considering no retransmission can improve the battery life of IoT devices, at the cost of a lower Quality of Service (QoS).

@@

% ----------------------------------------------------------------------------
% \section{Motivations for Selfish MAB Learning for IoT Networks}
\section{Introduction}
\label{sec:4:motivations}
% ----------------------------------------------------------------------

>>>>

\abstractStartChapter{}%
%
In this chapter, we propose two models of Internet of Things (IoT) networks, composed of many independent IoT end-devices,
that can use low-cost RL (Reinforcement Learning) algorithms to learn to improve their spectrum access.
%
Decentralized RL for IoT lets the devices use acknowledgements sent by their Base Station as a reward, instead of sensing feedback like for OSA.
We consider many independent ``dynamic'' devices, communicating with a small probability at every instant.
Simulations show that dynamic devices can improve their spectrum efficiency,
by using MAB algorithms like \UCB.
% in the case of a non-uniform repartition of the static devices in the channels
We also developed a proof-of-concept using USRP platforms, for a real-world validation of this approach.
% Numerical simulations justify the interest of the approach,
%  of the advantage of using MAB algorithms for the first model.
%
% On a simple example, we present in Section~\ref{sec:4:gnuradio} a demonstration that implements and validates the proposed approach, using real wireless radio hardware.
The first model
% without retransmission of packets,
is interesting for its simplicity,
and because considering no retransmission can improve the battery life of IoT devices, at the cost of a lower Quality of Service (QoS).

@@

% ----------------------------------------------------------------------------
% \section{Motivations for Selfish MAB Learning for IoT Networks}
\section{Introduction and motivations for MAB learning for IoT Networks}
\label{sec:4:motivations}
% ----------------------------------------------------------------------

### 2019-06-15 2-Chapters/5-Chapter/chapter5.tex
\vfill{} before \minitoc at beginning of all Chapters
Small improvements on layout of abstract/minitoc for chapters
Lots of small changes. I'll start fixing Chapter 2 this weekend, today my goal is Ch1
Better links to
- https://SMPyBandits.GitHub.io/MultiPlayers.html
- https://SMPyBandits.GitHub.io/NonStationaryBandits.html
Typo

\paragraph{Abstract.}
%
In this Chapter~\ref{chapter:5}, we are interested in a more formal approach to the decentralized learning problem presented in Chapter~\ref{chapter:4}.
We restrict to the easier case of at most $M \leq K$ devices in a network with $K$ channels, because it was found very hard to analyze the aforementioned IoT network model.
%
We discuss three feedback levels that give variants of the multi-players MAB model previously studied in the literature.
Using a decomposition of the centralized system regret, we start by explaining the intuition about what an efficient decentralized algorithm should do, and then we propose \RandTopM{} and \MCTopM, two new orthogonalization schemes.
Combining them with the \klUCB{} index policy gives order-optimal algorithms, that achieve state-of-the-art performance,
as illustrated by numerical simulations.
We conclude by reviewing different extensions of the multi-players models.

% \TODOL{C'est bizarre ce problème d'espacement vertical ici... je ne sais pas comment le corriger !}

\minitoc
% ----------------------------------------------------------------------

\newpage

@@

The experiments in this chapter use SMPyBandits,
and we refer to the following page for details on how to reproduce them,\\
\href{https://SMPyBandits.GitHub.io/MultiPlayers.html}{\texttt{SMPyBandits.GitHub.io/MultiPlayers.html}}

>>>>

\abstractStartChapter{}%
%
In this chapter, we are interested in a more formal approach to the decentralized learning problem presented in Chapter~\ref{chapter:4}.
We restrict to the easier case of at most $M \leq K$ devices in a network with $K$ channels, because it was found very hard to analyze the aforementioned IoT network model.
%
We discuss three feedback levels that give variants of the multi-players MAB model previously studied in the literature.
Using a decomposition of the centralized system regret, we start by explaining the intuition about what an efficient decentralized algorithm should do, and then we propose \RandTopM{} and \MCTopM, two new orthogonalization schemes.
Combining them with the \klUCB{} index policy gives order-optimal algorithms, that achieve state-of-the-art performance,
as illustrated by numerical simulations.
We conclude by reviewing different extensions of the multi-players models.

\minitocStartChapter{}

@@

The experiments in this chapter use our library SMPyBandits, as presented in Chapter~\ref{chapter:3},
and we refer to the following page for details on how to reproduce them,
\href{https://SMPyBandits.GitHub.io/MultiPlayers.html}{\texttt{SMPyBandits.GitHub.io/MultiPlayers.html}}
